On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-16 Manuscript/manuscript.tex
removed space before my name
about student author and press summary

% Add author information below. Communicating author is indicated by an 
% asterisk, the affiliation is shown by superscripted lower case letter if 
% several affiliations need to be noted.
\author{
Mathew Chandy*, Elizabeth D. Schifano, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
Student: mathew.chandy@uconn.edu* \\
Mentors: elizabeth.schifano@uconn.edu, jun.yan@uconn.edu
}
\pagestyle{empty}
\begin{document}

@@

>>>>

% Add author information below. Communicating author is indicated by an 
% asterisk, the affiliation is shown by superscripted lower case letter if 
% several affiliations need to be noted.
\author{Mathew Chandy*, Elizabeth D. Schifano, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT \\ \medskip 
Student: mathew.chandy@uconn.edu* \\
Mentors: elizabeth.schifano@uconn.edu, jun.yan@uconn.edu
}
\pagestyle{empty}
\begin{document}

@@

\section*{About Student Author}
\label{sec:asa}
Mathew Chandy is a senior majoring in both Statistics and Statistical Data Science, 
and he plans to graduate in the spring of 2024.

\section*{Press Summary}
\label{sec:press}
This simulation study evaluates the sample size necessary to estimate the mean,
standard deviation, and lag-1 autocorrelation of a stationary time series using
different block bootstrap confidence interval types. The results showed that 
percentile-based confidence intervals for the lag-1 autocorrelation may suffer 
from coverage deterioration as 
sample size is increased, motivating the authors to propose a new recentered percentile 
confidence interval which does not deteriorate in performance for greater sample sizes.
The results also suggest that when using Student's $t$ bootstrap confidence intervals, 
a sample size of at least 1600 may be sufficient to estimate the mean, 
whereas a sample size larger than 3200 may be necessary to estimate 
the standard deviation. Finally, to estimate the lag-1 autocorrelation, using
Student's $t$ bootstrap confidence intervals demands a sample size of at least 100 
when the marginal distribution is standard normal and a sample size of at least 1600 when
the marginal distribution is unit exponential.
